\documentclass{article}
\usepackage{ocgx}
% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{{Algorithms SV worksheet 3}}
\author{Bálint Molnár}

\begin{document}
\maketitle


\section{Trees}

\begin{enumerate}
   \item Prove that, in a binary search tree, if node n has two children, then
its successor has no left child.
\item Prove that in a BST in which all nodes have either 0 or 2 children, if a key is not in a bottom node, its successor, if it exists, must be.
\item Explain insertion and deletion to a red-black tree. Please use figures instead of just writing pseudocode.

\end{enumerate}

\section{Hash Tables}

\begin{enumerate}
    \item Make a hash table with 8 slots and insert into it the following values:
15, 23, 12, 20, 19, 8, 7, 17, 10, 11.\\
Use the hash function 
h(k) = (k mod 10) mod 8,
and resolve collisions by chaining
\item How can you handle deletions from an open addressing table? What are the
problems with the obvious naïve approach?
\item One idea to avoid handling collisions is to make the hash table large enough so that the chances of having a collision are negligible. Explain why it is not feasible.\\
\emph{Hint: Birthday problem}

\item Find another use of hash functions in Computer Science/Software Engineering. Explain what properties of hash functions are required for this use case, and why you also need them for hash tables.
\end{enumerate}
\section{Algorithm Design}
Solve this \href{https://leetcode.com/problems/lru-cache/description/}{Leetcode problem}. You can use any programming languages (Python, Java or C++ preferred). Please send your code, with an explanation of your algorithm.\\
\emph{This is a very standard coding interview question, so you might be tempted to just look up the solution. Please attempt it first without any help.}


\end{document}